Inferential Analysis of the \\ Supreme Court Citation Network

### 2018-01-03 NetworkVisualizations/visualizations.tex
updated slides

>>>>

\newpage
\begin{figure}[!htb]
	\begin{center}
		\includegraphics[width=0.9\textwidth]{{citations.trans}.pdf}
		\caption{Illustration of transitivity in the Supreme Court citation network. This is a subnetwork consisting of cases 377 U.S. 184, 491 U.S. 1, and 517 U.S. 44, highlighted in yellow; and the cases that cite and are cited by these three cases. The transitive structure formed by the three named cases is highlighted in pink.}
	\end{center}
\end{figure}

\newpage
\begin{figure}[!htb]
	\begin{center}
		\includegraphics[width=0.9\textwidth]{{citations.recip}.pdf}
		\caption{Illustration of reciprocity in the Supreme Court citation network. This is a subnetwork consisting of cases 472 U.S. 353 and 472 U.S. 400, highlighted in yellow; and the cases that cite and are cited by these two cases. Reciprocal ties are highlighted in pink.}
	\end{center}
\end{figure}

\newpage
\begin{figure}[!htb]
	\begin{center}
		\includegraphics[width=0.9\textwidth]{{citations.pop}.pdf}
		\caption{Illustration of popularity in the Supreme Court citation network. This is a subnetwork consisting of all cases contained in volume 369 of the U.S Supreme Court Reporter of Decisions, which are highlighted in yellow, and the cases that cite these cases. Case 369 U.S. 186, discussed in the text, is highlighted in pink.}
	\end{center}
\end{figure}

\newpage
\begin{figure}[!htb]
	\begin{center}
		\includegraphics[width=0.9\textwidth]{{citations.soci}.pdf}
		\caption{Illustration of reciprocity in the Supreme Court citation network. This is a subnetwork consisting of all cases contained in volume 466 of the U.S Supreme Court Reporter of Decisions, which are highlighted in yellow, and the cases that are cited by these cases. Case 466 U.S. 789, discussed in the text, is highlighted in pink.}
	\end{center}
\end{figure}

### 2018-01-03 Tex/presentations/SPSA2018/DesmaraisSPSATalk.tex
updated slides

\documentclass[handout]{beamer}
\usepackage{bm}
\usepackage{listings}
\usepackage{algorithmic}
\usepackage{verbatim}
\usepackage{rotating}
\usepackage{multirow}
\lstloadlanguages{R}
\lstset{ language=R, basicstyle=\scriptsize\ttfamily, commentstyle=\ttfamily\color{gray}, numbers=left, numberstyle=\ttfamily\color{gray}\footnotesize, stepnumber=1, numbersep=5pt, backgroundcolor=\color{white}, showspaces=false, showstringspaces=false, showtabs=false, frame=single, tabsize=2, captionpos=b, breaklines=true, breakatwhitespace=false, escapeinside={}, keywordstyle={}, morekeywords={} }\renewcommand{\P}{\mathcal{P}}
\newcommand{\bt}{\pmb{\theta}}
\newcommand{\bG}{\pmb{\Gamma}}
\newcommand{\p}{\pause}
\newcommand{\pitem}{\pause \item}
\newcommand{\N}{\mathcal{N}}
\newcommand{\Y}{\bm{\mathcal{Y}}}
\newcommand{\bh}{\bm{h}} 
\DeclareMathOperator*{\argmax}{arg\,max}

@@

%\affil[1]{University of Massachusetts Amherst}
%\affil[2]{University of Connecticut}

@@

\begin{frame} \frametitle{Two Limitations in Case-Level Analysis}

@@

@@

\begin{frame} \frametitle{Transitivity}

@@

\begin{frame} \frametitle{Popularity and Sociality}

@@

@@

\begin{frame} \frametitle{Results Dependence}

\begin{frame} \frametitle{Results Covariates}

@@

>>>>

\documentclass[handout]{beamer}
\usepackage{bm}
\usepackage{colortbl}
\usepackage{listings}
\usepackage{algorithmic}
\usepackage{verbatim}
\usepackage{rotating}
\usepackage{booktabs}
\usepackage{multirow}
\lstloadlanguages{R}
\lstset{ language=R, basicstyle=\scriptsize\ttfamily, commentstyle=\ttfamily\color{gray}, numbers=left, numberstyle=\ttfamily\color{gray}\footnotesize, stepnumber=1, numbersep=5pt, backgroundcolor=\color{white}, showspaces=false, showstringspaces=false, showtabs=false, frame=single, tabsize=2, captionpos=b, breaklines=true, breakatwhitespace=false, escapeinside={}, keywordstyle={}, morekeywords={} }\renewcommand{\P}{\mathcal{P}}
\newcommand{\bt}{\pmb{\theta}}
\newcommand{\bG}{\pmb{\Gamma}}
\newcommand{\p}{\pause}
\newcommand{\pitem}{\pause \item}
\newcommand{\N}{\mathcal{N}}
\newcommand{\Y}{\bm{\mathcal{Y}}}
\newcommand{\bh}{\bm{h}} 
\DeclareMathOperator*{\argmax}{arg\,max}

@@

@@

\begin{frame} \frametitle{Two Limitations in Case-Level Analysis}
\Large
\begin{enumerate}
\item {\bf Theoretical:} Cannot learn about relational processes
\\~\\
\item {\bf Methodological:} Risk bias from omitted structure
\end{enumerate}

@@

\centering

\includegraphics[width = 0.95\textwidth,trim= 0cm 1cm 0cm 2cm,clip=true ]{../../../NetworkVisualizations/citations_recip.pdf}

@@

\begin{frame} \frametitle{Transitivity}
\centering

\includegraphics[width = 0.95\textwidth,trim= 0cm 1cm 0cm 2cm,clip=true ]{../../../NetworkVisualizations/citations_trans.pdf}

@@

\begin{frame} \frametitle{Popularity and Activity}

\centering

\includegraphics[width = 0.95\textwidth,trim= 0cm 3cm 6cm 8cm,clip=true ]{../../../NetworkVisualizations/citations_pop.pdf}

@@

\begin{frame} \frametitle{Data}

\begin{columns}
\begin{column}{4cm}
\scalebox{0.8}{
\begin{tabular}{|
>{\columncolor[HTML]{C0C0C0}}l |l|l|}
\hline
{\color[HTML]{333333} } & \cellcolor[HTML]{C0C0C0}{\color[HTML]{333333} Terms} & \cellcolor[HTML]{C0C0C0}{\color[HTML]{333333} Cases} \\ \hline
CE Hughes*              & 1937 - 1941                                          & 629                                                                                                                  \\ \hline
HF Stone                & 1942 - 1946                                          & 766                                                                                                                \\ \hline
FM Vinson               & 1946 - 1953                                          & 788                                                                                                                  \\ \hline
E Warren                & 1954 - 1969                                          & 2159                                                                                                                  \\ \hline
WE Burger               & 1970 - 1986                                          & 2805                                                                                                                   \\ \hline
W Rehnquist**            & 1987 - 2001                                          & 1670                                                                                                                 \\ \hline
\end{tabular}
}
\end{column}
\begin{column}{6cm}
\includegraphics[scale=0.15,clip=true,trim=.5cm 0cm 0cm 2cm]{../../../NetworkVisualizations/citations1}
\end{column}

\end{columns}

@@

\begin{frame} \frametitle{Results: Dependence}
\begin{changemargin}{-1cm}{-1cm}
\centering
 \begin{tabular}{cc}

    Reciprocity &  Transitivity \\
\includegraphics[width = 0.55\textwidth, trim= 1cm 1cm 0.5cm .45cm,clip=true]{../../images/mutual_coef_trend.pdf} & \includegraphics[width = 0.55\textwidth, trim= 1cm 1cm 0.5cm .45cm,clip=true]{../../images/triangle_coef_trend.pdf} \\

     Activity & Popularity \\
\includegraphics[width = 0.55\textwidth, trim= 1cm 1cm 0.5cm .45cm,clip=true]{../../images/o2star_coef_trend.pdf} & \includegraphics[width = 0.55\textwidth, trim= 1cm 1cm 0.5cm .45cm,clip=true]{../../images/i2star_coef_trend.pdf} \\

\end{tabular}

\end{changemargin}
\end{frame}

\begin{frame} \frametitle{Results: Covariates}
\begin{changemargin}{-1cm}{-1cm}
\centering

 \begin{tabular}{cc}
  MQ Score Difference & Ideological Breadth \\
\includegraphics[width = 0.55\textwidth, trim= 1cm 1cm 0.5cm .45cm,clip=true]{../../images/mq_coef_trend.pdf} & \includegraphics[width = 0.55\textwidth, trim= 1cm 1cm 0.5cm .45cm,clip=true]{../../images/absdiffmq_coef_trend.pdf} \\

   Same Issue &  Majority Size \\
\includegraphics[width = 0.55\textwidth, trim= 1cm 1cm 0.5cm .45cm,clip=true]{../../images/sameissue_coef_trend.pdf} & \includegraphics[width = 0.55\textwidth, trim= 1cm 1cm 0.5cm .45cm,clip=true]{../../images/numberjusticespro_coef_trend.pdf} \\

\end{tabular}

\end{changemargin}
\end{frame}

@@

\begin{tabular}{rllll}
\hline \hline
& \multicolumn{2}{c}{Independent Model} & \multicolumn{2}{c}{Full Model} \\
  \hline
 & mean & range & mean & range \\ 
  \hline
precision & 0.5499 & (0.5384, 0.5619) & 0.8605 & (0.8526, 0.8666) \\ 
  recall & 0.0827 & (0.0811, 0.0843) & 0.5858 & (0.5817, 0.5891) \\ 
  F1 score & 0.1438 & (0.141, 0.1463) & 0.6971 & (0.6941, 0.7008) \\ 
   \hline \hline
\end{tabular}
